Token-level author diarization using clustering of stylistic contexts

### 2017-06-01 paper/paper.tex
Setup c partialy finished.

For task \emph{c}

>>>>

For task \emph{c} we should have somehow determine the number of clusters. Due to lack of time we decided to test algorithms which can determine this number automatically, i.e. this is not a hyperparameter which should be known in advance. Since we noticed that grid searches take a lot of time, we reduced a training set from 50\% to 10\% and repeated all experiments. We tested DBSCAN, affinity propagation, and mean shift algorithms.

The best results were obtained with DBSCAN, and for other ones they were very low. We noticed that the estimated number of clusters with the best hyerparameters (eps=100, min\_samples=71, metric=manhattan) was in almost every case greater than a real one, and solid number of examples were not even clustered because they were not close enough to any core sample to be a part of a cluster. In all grid searches we used BCubed F measure and only DBSCAN achieved acceptable level. Our opinion is that this was a consequence of a larger number of smaller clusters which had a positive influence on BCubed precision and therefore on overall performance.

Since the relatively good Bcubed F measure is not of practical use in real life appliactions if the number of clusters is always wrongly estimated, we decided to repeat the grid search for DBSCAN, but now we set the Calinski-Harabaz index as evaluation measure since it does not require the real number of clusters for clustering evaluation. Finally, from all results on training set we chose (eps=0.23, min\_samples=64, metric=cosine) for the final hyperparameters. This wasn't the best combination, but it produced relatively acceptable amount of noisy (non-clustered) elements per document.

Što s noisy opisati.
